SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-11-07 docs/questioning.tex
some changes

{\it Diglossia}~\cite{SMS13} combines positive taint tracking (see
Subsubsection~\ref{sec:taint}) together with parse-tree validation.
Diglossia was based on the theory of Ray and Ligatti~\cite{RL12b}
(also see Section~\ref{sec:attacks}) to detect {\sc dsl} code
injection attacks. In addition, it is actually the first, and so far
the only framework that detects No{\sc sql} injection attacks. When an
application computes an output string (query), Diglossia computes a
``shadow" of this string. Specifically, it maps all characters
introduced by the application to a shadow character set. This set does
not contain any characters coming from the tainted input. Then, the
scheme creates the tree of the query that is about to be executed and
compares it with the parsed tree of the ``shadow" (locus {\sc z}). If
the trees are not equal the application is probably under attack. Note
that Diglossia can be bypassed in the same way as other taint
tracking approaches and is described in reference~\cite{NBR14}.
%% PL which way is this exactly?

@@

	&   {\it libAnomaly}~\cite{VMV05} & 226 & (344,15646,60,0)\_r & +1{\it ms} ({\sc s}) & {\sc sql} injection \\

@@

  & 	{\it {\sc swap}}~\cite{WPLKK09} & 52 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & $\sim$180\% ({\sc s}) & {\sc xss} \\ 

>>>>

{\it Diglossia}~\cite{SMS13} combines positive taint tracking (see
Subsubsection~\ref{sec:taint}) together with parse-tree validation.
Diglossia was based on the theory of Ray and Ligatti~\cite{RL12b}
(also see Section~\ref{sec:attacks}) to detect {\sc dsl} code
injection attacks. In addition, it is actually the first, and so far
the only framework that detects No{\sc sql} injection attacks. When an
application computes an output string (query), Diglossia computes a
``shadow" of this string. Specifically, it maps all characters
introduced by the application to a shadow character set. This set does
not contain any characters coming from the tainted input. Then, the
scheme creates the tree of the query that is about to be executed and
compares it with the parsed tree of the ``shadow" (locus {\sc z}). If
the trees are not equal the application is probably under attack. Note
that Diglossia can be bypassed in the same way as other taint
tracking approaches as described in reference~\cite{NBR14}.
%% PL which way is this exactly?

@@

	&   {\it libAnomaly}~\cite{VMV05} & 226 & (344,15646,60,0)\_r & 1{\it ms} ({\sc s}) & {\sc sql} injection \\

@@

  & 	{\it {\sc swap}}~\cite{WPLKK09} & 52 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & up to 261 {\it ms} ({\sc s}) & {\sc xss} \\ 
